Supplemental Information

### 2021-02-13 supp_v1.Rmd
message

---
title: "Supplemental Information"
author: "CB Brinkerhoff, CJ Gleason, PA Raymond, MH Harlan"
date: "`r Sys.Date()`"
csl: APA.csl
output:
  word_document: 
      reference_docx: word-styles-reference.docx
bibliography: References.bib

>>>>

---
title: "Supplemental Information"
author: "CB Brinkerhoff, CJ Gleason, PA Raymond, MH Harlan"
date: "`r Sys.Date()`"
csl: american-geophysical-union.csl
output:
  word_document: 
      reference_docx: word-styles-reference.docx
bibliography: References.bib
